Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Clarify section reference

The idea behind the mask is to distort the grid of the FDM by reproducing the intersection surface between $M$ and the free surface.
Here, free surface refers to the ambient waves of Tessendorf's method \ref{sec:oceanWaves} plus the interactive waves generated by all solids except $M$.
It does \textbf{not} include the free surface generated by $M$, or the simulation would face a divergence issue.

>>>>

The idea behind the mask is to distort the grid of the FDM by reproducing the intersection surface between $M$ and the free surface.
Here, free surface refers to the ambient waves of Tessendorf's method (see Section \ref{sec:oceanWaves}) plus the interactive waves generated by all solids except $M$.
It does \textbf{not} include the free surface generated by $M$, or the simulation would face a divergence issue.
